---
title: "Datasets"
format:
  html:
    df-print: paged
---

```{r}
#| echo: false
#| message: false
library(tidyverse)
```

## Primary Datasets

### Drug Consumption

Real data on 1,876 participants' demographics, personality traits, and substance use. Used in Walkthrough #1 to predict cocaine use (`Coke`, classification).

<a href="https://jmgirard.github.io/tips2022ml/data/drug_consumption.csv"><button type="button" class="btn btn-primary">Download CSV</button></a>

```{r}
#| echo: false
#| message: false
#| eval: true
read_csv("./data/drug_consumption.csv")
```

### California Housing

Real data on 2,000 blocks in California from 1990 about houses, population, and location. Used in Walkthrough #2 to predict median house value (`house_mdn_value`, regression).

<a href="https://jmgirard.github.io/tips2022ml/data/calihousing.csv"><button type="button" class="btn btn-primary">Download CSV</button></a>

```{r}
#| echo: false
#| message: false
#| eval: true
read_csv("./data/calihousing.csv")
```

## Additional Datasets

### Airline Satisfaction

Real data on the satisfaction and experience of 10,000 customers of an airline. Can be used to predict satisfaction status (`satifaction`, classification).

<a href="https://jmgirard.github.io/tips2022ml/data/airsat.csv"><button type="button" class="btn btn-primary">Download CSV</button></a>

```{r}
#| echo: false
#| message: false
#| eval: true
read_csv("./data/airsat.csv")
```

### Titanic Disaster

Real data on 1,309 passengers on the Titanic. Can be used to predict survival (`survived`, classification) or ticket price (`fare`, regression).

<a href="https://jmgirard.github.io/tips2022ml/data/titanic.csv"><button type="button" class="btn btn-primary">Download CSV</button></a>

```{r}
#| echo: false
#| message: false
#| eval: true
read_csv("./data/titanic.csv")
```

### Water Potability

Real data on the potability and chemical properties of 2,011 water bodies. Can be used to predict safety to drink (`Potability`, classification).

<a href="https://jmgirard.github.io/tips2022ml/data/water.csv"><button type="button" class="btn btn-primary">Download CSV</button></a>

```{r}
#| echo: false
#| message: false
#| eval: true
read_csv("./data/water.csv")
```
